DNSKEY Management

### 2012-12-10 paper/paper.tex
Fix some TODOs in paper

%% TODO you cannot talk about TARs here without explaining. Reference
%% for this?
DNSSEC's trust hierarchy is similar to the SSL Certificate infrastructure, where an entity marks its trust in another by \emph{signing} its certificate\footnote{Which is nothing more than a public key with additional metadata.}. However, DNSSEC theoretically only has one single top-authority\footnote{The use of TAR's should remain temporary, as in an ideal setup DNSSEC could work without them.}, while the SSL Certificate hierarchy disposes of many.

@@

Another type of TAR resides at the resolver: a statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, an addition
%% TODO what does this "plugin" do exactly?
to a standard resolver, \cite{Osterweil09} which can poll keys from
different locations such as web pages, but also also other
vantage-enabled resolvers. Of course, the operator may also choose to
add trusted keys manually.

@@

%% TODO add part about computation

>>>>

DNSSEC's trust hierarchy is similar to the SSL Certificate infrastructure, where an entity marks its trust in another by \emph{signing} its certificate\footnote{Which is nothing more than a public key with additional metadata.}. However, DNSSEC theoretically only has one single top-authority, while the SSL Certificate hierarchy disposes of many.

@@

Another type of TAR resides at the resolver: a statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, a standalone
daemon, \cite{Osterweil09} which can poll keys from different
locations such as web pages, but also from other vantage resolvers. Of
course, the operator may also choose to add trusted keys manually.

@@
